Linting Linearity in Core/System FC

### 2023-01-02 report.tex
Chapters and sections in report document

\documentclass[a4paper, draft]{article}

@@

\begin{document}
\maketitle

% \section{Introduction}

% \subsection{Motivation}

% \begin{itemize}
%     \item Are we really preserving linearity?
%     \item Inform/unlock other optimisations that take into account linearity
% \end{itemize}

% \section{Background}

@@

% \section{Related Work}

% \section{Technical Details}

\section{Foreword}

This document is a work in progress proposal that I will deliver (in an extended
form) at the end of the semester as part of my master thesis preparation. The
document still needs a proper introduction, lengthy background and related work
section  such that an outsider might understand what I propose to do. However,
this initial iteration is instead targeted at those already familiar with the
problem and serves as a (less bureaucratic) proposal on linting linearity in
Core and to showcase the preliminary progress I have made so far.

>>>>

\documentclass[a4paper, draft]{report}

@@

\begin{document}
\maketitle
\tableofcontents

\chapter{Introduction}

\subsection{Motivation}

\begin{itemize}
    \item Are we really preserving linearity?
    \item Inform/unlock other optimisations that take into account linearity
\end{itemize}

\chapter{Background}

\section{Linear Types}

\section{Haskell}

\section{Linear Haskell}

\section{Core Haskell}

\section{GHC Pipeline}

@@

\chapter{Related Work}

\section{System FC}

\section{Linear Haskell}

\chapter{Technical Details}

% \section{Foreword}

% This document is a work in progress proposal that I will deliver (in an extended
% form) at the end of the semester as part of my master thesis preparation. The
% document still needs a proper introduction, lengthy background and related work
% section  such that an outsider might understand what I propose to do. However,
% this initial iteration is instead targeted at those already familiar with the
% problem and serves as a (less bureaucratic) proposal on linting linearity in
% Core and to showcase the preliminary progress I have made so far.
